Sr: Processing Data Streams and Avoiding Work

### 2012-05-04 paper/paper.tex
Unbreak captions

\begin{figure}
\begin{verbatim}
                  |--------|
                - | worker |
               /  |--------|
|-----------| /   |--------|
| master    | --- | worker |
| spout     |     |--------|
| fetcher   |     |--------|
| collector | --- | worker |
|-----------| \   |--------|
               \  |--------|
                - | worker |
                  |--------|
\end{verbatim}
\caption{Topology of the test Sr cluster used in the word count case study.\\
Each box is a single machine.}
\label{fig:clusterDiagram}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{long-tail-ranks.png}
\caption{The frequencies of words in the Wikipedia Featured Articles corpus\\
have a long-tailed distribution.}
\label{fig:wordDist}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{top-100-precision.png}
\caption{Number of top 100 results returned in the top-100 by the word count job}
\label{fig:precision}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{f-score.png}
\caption{$F_{0.5}$-score for the top-100 word count job. I measured the $F$-score with\\
$\beta=0.5$ because the goal of the job is to run a top-k filter on it, meaning I care more\\
about precision than recall.}
\label{fig:fscore}
\end{figure}

@@

>>>>

\begin{figure}
\begin{verbatim}
                  |--------|
                - | worker |
               /  |--------|
|-----------| /   |--------|
| master    | --- | worker |
| spout     |     |--------|
| fetcher   |     |--------|
| collector | --- | worker |
|-----------| \   |--------|
               \  |--------|
                - | worker |
                  |--------|
\end{verbatim}
\caption{Topology of the test Sr cluster used in the word count case study. Each box is a single machine.}
\label{fig:clusterDiagram}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{long-tail-ranks.png}
\caption{The frequencies of words in the Wikipedia Featured Articles corpus have a long-tailed distribution.}
\label{fig:wordDist}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{top-100-precision.png}
\caption{Number of top 100 results returned in the top-100 by the word count job.}
\label{fig:precision}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{f-score.png}
\caption{$F_{0.5}$-score for the top-100 word count job. I measured the $F$-score with $\beta=0.5$ because the goal of the job is to run a top-k filter on it, meaning I care more about precision than recall.}
\label{fig:fscore}
\end{figure}

@@

\section{Discussion}
\label{sec:discussion}

\bibliography{sr}{}
\bibliographystyle{plain}
